Improving Multi-Domain Neural Machine Translation by Differential Data Selection

### 2021-01-25 2021/acl-ijcnlp2021/mdmt.tex
add algo

\title{}

@@

\bibliographystyle{acl_natbib}
\bibliography{acl2021}

%\appendix

\end{document}

>>>>

\title{Improving Multi-Domain Neural Machine Translation by Differential Data Selection}

@@

\section{Introduction}\label{sec:intro}

\section{Formalizing multi-domain translation}
\begin{algorithm}[h!]
\caption{Multi-domain Training} \label{alg:mdmt}
\label{alg:multidomain}
\begin{algorithmic}[1]
\REQUIRE {
\begin{itemize}
	\item Corpora $C^i, i\in [1,..,K]$ for $K$ domains.
	\item Dev sets $Dev^i, i\in [1,..,K]$ for $K$ domains.
	\item Importance weights of domains in the final evaluation $\lambda_{t,d}^i, i\in [1,..,K]$
	\item Batch size $B$.
	\item Temporal Data Selection Distribution(T-DSD)$$P_{\system{T-DSD}}(t)(x,y)=\sum_{i}\lambda_{l,d}^i(t)P_i(t)(x,y)$$
	\item $Eval\_scores = []$
	\item $Early\_stopping$ criterion.
\end{itemize}}
\REPEAT 
\STATE{Iteration t.}
\STATE{Randomly pick $i \in [1,..,K]$ w.r.t  $[\lambda_{l,d}^1 \dots \lambda_{l,d}^K](t)$.}
\STATE{Sample $B$ sentences from $C^i$ with empirical distribution $P_i(t)(x,y)$.}
\STATE{Update model by applying SGD computed from $B$ sampled sentences.}
\IF{$t \equiv 0 \mod{eval\_step}$}
	\STATE{Evaluate current model with K dev sets. Denote $S_t^i$ performance of model at iteration t on domain i.}
	\STATE{Report weighted score using Domain Importance Weights(DI-Weights) $\lambda_{t,d}^i, i\in [1,..,K]$. $$eval(t) = \displaystyle{\mathop{\sum}_i \lambda_{t,d}^i S_t^i}$$}
	\STATE{$Eval\_scores.append(eval(t))$.}
\ENDIF
\IF{$Early\_stopping(Eval\_scores)$}
	\STATE{Stop training loop.}
\ENDIF
\UNTIL{convergence}
\end{algorithmic}
\end{algorithm}
\section*{Acknowledgments}
\bibliographystyle{acl_natbib}
\bibliography{multidomain}
%\appendix
\end{document}
